Hysteresis in human computation:\\ how one task affects another

### 2015-01-07 docs/publications/2014.09_SCIENCE/man.tex
add chi2 analysis, work on manuscript

Faced with the ever-growing scale and complexity of data, researchers and
industry are increasingly relying on \textit{human computation} as a means
to extract useful knowledge.  Microtask
platforms, like Amazon Mechanical Turk, act like a human compute server,
making it possible to access human cognition quickly and inexpensively. 
This has lead to broad adoption across a spectrum of disciplines
in the social sciences and computer science, as well as in research into 
medical imaging technologies and other applications where expert opinion 
would normally be sought.  Here we show that an inherent
feature of microtask platforms and most crowdsourcing settings---the 
repetition of similar tasks---acts as a strong, but as yet unexplored source 
of bias.  These \textit{intertask effects} rival the
severity of overtly framing a task's purpose.  
Using image-labeling as a canonical microtask, we show that prior 
tasks influence the content that workers focus on, and the richness and
specialization of their vocabulary.    
While intertask effects can be a source of systematic bias, our
results suggest that, when properly controlled, they might be leveraged
to hone worker focus and specificity, and could play a key role in designing 
tasks that elicit expert-level judgments.
\end{sciabstract}

@@

While microtask platforms have been widely adopted as a research tool,
computer scientists also hold such platforms as the object of 
research, viewing  microtask platforms as a new kind of computing 
architecture.  In analogy to CPUs (central 
processing units) and GPUs (graphics processing units), 
Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
Meanwhile, researchers have sought to define a basic HPU instruction set, and
libraries for HPU programming are under active development
 \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.

Given the increasing prevalence of microtask-based research methods, there
is a desire to understand factors affecting the reliability of HPU
outputs.  Researchers have investigated task-design parameters such as the 
level of pay \cite{kazai2013analysis}, the training \cite{le2010ensuring} and 
pre-screening \cite{paolacci2010running} of workers, and user-interface 
design factors \cite{Finnerty2013}.  
Researchers have also investigated \textit{framing} effects, 
such as the effects of describing the workflow context 
\cite{Kinnaird2012281}, the purpose of tasks 
\cite{chandler2013breaking}, or altering the problem description
\cite{thibodeau2013natural}.  Results in psychology show that people are 
susceptible to various kinds of priming 
\cite{BJOP1796,No2007,beller1971priming}, and, in particular, 
task-repetition effects \cite{Gass1999549,sohn2001task}.  
Yet to our knowledge, no study has investigated the practical ramifications 
of intertask effects on human computation. The experiments we 
present here show that, unlike CPUs and GPUs, HPUs are subject to 
\textit{hysteresis}, meaning that their outputs depend on the 
\textit{history} of their inputs.

We investigated intertask effects using image-labeling tasks on the Amazon 
Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  This trend will probably continue 
in the long term because of their role in computer vision research 
\td{find another application} \cite{5543192}.  In microtask platforms, it is typical for work to be divided 
into bundles; on MTurk, these bundles are called Human Intelligence Tasks 
(HITs). Because of this bundling pattern, even if workers perform only one 
HIT, the opportunity for intertask effects arises.  For clarity, 
we will use ``task'' to mean the smallest repeatable unit of work, which, 
in our study, consists of labeling a single image.

In our first experiment, which we will refer to as 
\textit{intertask-food-objects}, workers were either assigned to the 
\textit{food} or \textit{objects} treatment.  Workers in these treatments
performed a set of five \textit{initial tasks}, which involved labeling
images depicting either food or (non-food) objects, depending on the worker's 
treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
tasks, workers performed five \textit{test tasks}, which were identical for 
both treatments.  The test tasks contained images depicting a 
mixture of food and other objects (see Fig.~\ref{fig:task}C).  Five initial 
tasks, together with the test tasks, comprised one HIT 
(\# workers were only allowed to participate once). During the HIT, workers 
were presented images one at a time, and, crucially, there was no distinction
or interruption between the initial and test tasks.

A $\chi^2$ test (\#) shows that the frequency of word usage by
workers in the \textit{food} and \textit{objects} treatments differed
significantly during test tasks, even though the test tasks were identical 
for the treatments.  This shows that earlier tasks have a 
significant effect on later ones, and raises concerns about the 
design of microtasks, and possibly the microtask methodology itself.

While this affirms the \textit{existence} of intertask effects, we wish to
understand the nature and severity of the bias induced by prior task 
exposure.  To formalize a notion of the extent of bias, we must first 
acknowledge that workers' responses to microtasks
carry an element of stochasticity: two workers will not, in general, provide
the same response to a given task.  Because worker responses are stochastic,
we take the extent of bias, $\theta$, to be the total shift in probability 
mass, for giving certain responses (i.e. certain words),
caused by a perturbation like intertask effects (\# in other words, the 
bias is the L1-distance between the probability distributions for responses
under one treatment, to that for responses under another.)

It is difficult to measure the change in a probability distribution based on
samples alone (\#), so we reformulate the problem slightly. Consider that,  
no matter the ultimate purpose of a microtask study, a microtask response
is used in \textit{some kind} of subsequent decision or 
further processing.
We denote this downstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
takes a microtask response as input, biases in the microtask response will 
in general lead to biases in the output of $\mathcal{D}$.  
We can make use of this fact, to estimate the bias, 
by placing a machine learning algorithm (a classifier), in the role of 
$\mathcal{D}$.  This classifier takes as input a worker's responses to test 
tasks, from which it learns to infer the worker's treatment 
(i.e. the initial tasks she was given). 
Intuitively, the classifier's ability to infer worker treatments
depends on how strongly prior tasks affect responses to 
subsequent ones.  Formally, the bias, $\theta$, is bounded 
by the accuracy of the classifier, $\eta$ (\#):
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
Thus, measuring the performance of the classifier allows us to establish a
lower bound on the extent of bias. This approach can be used to bound the 
bias induced by any perturbation, including both intertask effects and 
framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
(or 100\%) (meaning that the change of initial tasks induced a completely 
different set of responses to test tasks).

@@

Using a na\"ive Bayes classifier (\# in the 
supplementary material we discuss the choice of classifier, the
approach to measuring accuracy, and draw a comparison to the results obtained 
if a support vector machine is used.), we found a bias of 30\% between 
workers from the \textit{food} and \textit{objects} treatments, due to 
intertask effects.

As a point of comparison, we performed a similar experiment in which we 
framed the purpose of the tasks.  Workers were either told that the tasks 
were ``Funded by the laboratory for the visual perception of Food and 
Ingredients'', or ``\ldots of Objects and Tools''.  We did not observe a 
statistically significant framing-induced bias, using a na\"ive Bayes 
classifier (see Fig.~\ref{fig:theta}).  This suggests
that prior task exposure is a stronger priming modality than framing.

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (\#) (see Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin 
(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
strong bias (about 50\%; see Fig.~\ref{fig:theta}A) between the labels 
provided by workers from the two 
treatments during test tasks.  Again, we compared intertask effects to 
framing,
by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or cultures.  
For this framing experiment, we did not observe a statistically significant 
difference between the labels attributed by the \textit{food} and 
\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).

@@

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Bias as measured by a na\"ive Bayes classifier, $\theta_\mathrm{NB}$,
		induced in image-labeling tasks, due to framing and 
		intertask effects. 
		(A) Bias in the responses to five test tasks,
		measured between the pairs of treatments indicated on the abscissa.  
		(B) Bias between the treatments of \textit{task1}, 
		measured for individual test tasks, and plotted as a function of 
		task position.  Error bars show the 95\% confidence intervals.
	}
	\label{fig:theta}
\end{figure}

@@

To better understand the nature of 
intertask effects, we investigated the vocabulary
that workers used to label test tasks. A natural expectation is that, within
a given experiment, the food-primed workers would use more food-related words 
than their non-food-primed counterparts.  However, this was not generally 
the case. In the \textit{intertask-food-culture} experiment, food-primed
workers actually used significantly \textit{fewer} food-related words 
during test tasks
(\# food related words were identified using the wordnet corpus, augmented
with additional words obtained by crawling a recipe website (see supplementary
information for details)) (see Fig.~\ref{fig:specificity}).  This finding
rules out a simplistic conception of how intertask effects guide the worker's
attention.  It seems that when workers encounter content in 
prior tasks, the probability that they will refer to similar content in 
subsequent tasks changes significantly, although it does not necessarily 
increase.

To clarify this observation, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related words
used.
Both \textit{intertask} experiments showed that food-exposed workers had 
greater lexical richness, in reference to food, than their non-food-primed 
counterparts (as much as 20\% more; see Fig.~\ref{fig:specificity}).  This
held in the case of \textit{intertask-food-culture}, even though, in that 
experiment, food-primed workers referred to food less often overall.  
This enrichment of the food-related lexicon 
was also observed in the \textit{priming-food-objects}, and 
\textit{echo-food-objects} experiments, but to a lesser extent.

@@

\subsection*{S3: Additional results not shown in the main text}
		the top 5 most suppressed and most activated terms between treatment
		pairs.

@@

	\end{tabular}
	\caption{blah}
\end{table}

@@

	Before performing any analysis on the labels that workers provided, we
	performed a series of preprocessing steps.  
	\td{does this reflect the actual order in which the steps were done?}
	First, words wore lematized 
	using the
	\td{whatzit} lemmatizer.  This lemmatizer is very mild, tending only to 
	change plural words to their singular form.  Common
	words such as ``the'', ``to'', or ``with'', were found using the
	the \td{whatzit} stop-word list and removed.  Then, misspelled words were
	automatically corrected using a spelling correction algorithm described 
	below.  Finally, labels that contained
	multiple words (separated by spaces or punctuation) were split, with
	punctuation removed, and the separated words were treated as distinct 
	features in subsequent analysis.

@@

	\paragraph{Crawling the world food section of allrecipes.com.}
	The website allrecipes.com was accessed on 3-4 November 2014 using 
	automated scripts.  A total of 2642 recipe listings and 15621 recipe
	instruction pages were crawled.  Recipe listings were pages that provided 
	lists of recipes, and contained a title and short description for each.  
	The recipe instruction pages had lists of ingredients and preparation 
	instructions.  All of the words found in recipe titles, short
	descriptions, ingredients lists, and preparation instructions were
	collected, and saved as an auxiliary set to augment the \textit{legal set}
	used in spelling correction.

@@

We chose the synsets \textit{food.n.01} and \textit{food.n.02} to act as roots
in defining which words should be considered food-related.  Any word form
belonging to a synset which was a hyponym of one of the two root synsets
identified above was considered to be a reference to food.  Here, as in the
main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
of a hyponym, and so on.

@@

The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
and \textit{food.n.02} provide an extensive set of \td{X} words.  Manual
testing appeared to show that the coverage was very extensive, except in 
some cases references to ethnic foods were missing.  Since, especially in
\textit{exp2} we had images containing many ethnic foods, we decided to 
augment the wordnet corpus with words learned by crawling the world food
section of the allrecipes.com website.

After collecting a set of words using an automated script 
(\td{described above}), we collected the set of words that had been used by
workers and which had been seen during crawling of the allrecipes.com website,
but which were not included in wordnet.  We grafted these extra words into
the wordnet hyponym-hypernym graph manually, which ensured that any references
to ethnic words learned from crawling would be properly classified as 
food references.

\paragraph{Validation of the detection of food references.}
To determine whether our extended version of wordnet provided a good approach
to detecting food-related words, we sampled 500 words from the set of labels
produced by workers and had three human coders manually decide if they were 
food-related or not.  The method for randomly sampling the 500 words was 
described in above in \td{section number}.

The coders were instructed to consider whether a word was a noun signifying
an edible item.  The guiding principle was, for the coder to ask herself,
``can I eat this X'', where X is the word she is coding.  The coders were
shown the used in the task from which the word came, to help resolve ambiguity
in the sense of the word that had been given.  Coders were also shown the 
spelling correction (if any) that the spell-correction algorithm had made,
to help interpret misspelled words \td{we describe the spelling correction 
algorithm in section X}.

@@

	\textit{whether to correct misspelled words.}  Because we used free-text
	entry for the labels, there was bound to be many spelling mistakes.
	This would tend to reduce the accuracy of a classifier, because the 
	entries ``bread'' and ``braed'' would be regarded as completely different
	features, even though they clearly correspond to the same 
	\textit{intended word}.  While no algorithm can determine a worker's 
	intentions, it is possible to check words against a corpus, and, in the
	case of a misspelled word, look for plausible corrections based on 
	edit distance.

@@

	\textit{Whether to split multiple words.}  Although workers were 
	instructed to put one word per text input, many put multiple words.
	Theoretically the original multi-word entry might bear additional 
	information that could be useful in discerning a worker's exposure. 
	In practice, it would be necessary for that word combination to recur,
	which is unlikely.  Therefore we chose to split multi-word entries,
	using the individual words as features.  This meant that the outputs of
	some workers generated more features than those of others.

>>>>

Faced with the ever-growing scale and complexity of data, academic and 
industrial researchers are increasingly relying on \textit{human computation} 
as a means to extract useful knowledge.  Microtask
platforms, like Amazon Mechanical Turk, act like a human compute cluster,
making it possible to access human cognition quickly and inexpensively. 
This has lead to their broad adoption by social and computer scientists.  
Human computation is being used in applications
where expert opinion would normally be sought, such as in reviewing 
medical images.
Here we show that the repetition of similar tasks, which is an inherent
feature of microtask and crowdsourcing platforms, acts as a strong
and largely unexplored source of bias.  The effects of previous tasks on
later ones---\textit{intertask effects}---are more severe than the effects 
of framing, such as by disclosing a task's purpose.  
Using image-labeling, the canonical microtask, we show that prior 
tasks influence the content that workers chose to focus on, as well as the 
richness and specialization of their vocabulary.    
While intertask effects can be a source of systematic bias, our
results suggest that, when properly controlled, they might be leveraged
to hone worker focus and specificity, and could play a key role in engineering
tasks that elicit reproducible, expert-level judgments.
\end{sciabstract}

@@

While microtask platforms have been widely adopted as a research tool,
computer scientists also hold such platforms as the object of 
research, viewing  microtask platforms as a new kind of computing 
architecture.  In analogy to CPUs (central 
processing units) and GPUs (graphics processing units), 
Davis \textit{et al} invoked the \textit{human processing unit}, or HPU \cite{5543192}.
Researchers have sought to define a basic HPU instruction set, and
libraries for HPU programming are under active development
 \cite{little2010turkit,minder2011crowdlang,minder2012crowdlang,kittur2011crowdforge}.

Given the increasing prevalence of microtask-based research methods, there
is a desire to understand factors affecting the reliability of HPU
outputs.  Researchers have investigated task-design parameters such as the 
level of pay \cite{kazai2013analysis}, the training and pre-screening of 
workers \cite{le2010ensuring,paolacci2010running}, and user-interface 
design \cite{Finnerty2013}.  
Researchers have also investigated the effects of \textit{framing}, 
by altering the description of the workflow context 
\cite{Kinnaird2012281}, the purpose of tasks 
\cite{chandler2013breaking}, and the problem description
\cite{thibodeau2013natural}.

Microtasks are typically distributed to workers in bundles.  For example, a 
worker might be assigned a set of ten images, and asked to provide 
descriptive words (or \textit{labels}) for each.  
On MTurk, these bundles are called Human Intelligence Tasks (HITs).
But for the sake of clarity, we will use ``task'' to mean the smallest 
repeatable unit of work, which, in our study, consists of labeling a single
image.

Results in psychology show that people are susceptible to various kinds of 
priming \cite{BJOP1796,No2007,beller1971priming}, including 
task-repetition effects \cite{Gass1999549,sohn2001task}.  
Yet to our knowledge, no study has investigated the bias that might
result from the fact that microtask workers typically perform many tasks in 
succession.  The experiments we present here show that a worker's response 
to a task depends strongly on the tasks she had performed beforehand.
In other words, unlike CPUs and GPUs, HPUs are subject to 
\textit{hysteresis}, meaning that their outputs depend on the 
\textit{history} of their inputs.
We call the effects that prior tasks induce on later ones 
\textit{intertask effects}.

We investigated intertask effects using image-labeling tasks on the Amazon 
Mechanical Turk (MTurk) microtask platform.  Image-labeling tasks are among
the most common MTurk tasks \cite{chandler2013breaking,Berinsky2012351,Finnerty2013,paolacci2010running}.  This trend will probably continue 
in the long term because of their role in computer vision research 
\td{find another application} \cite{5543192}.  In our first experiment, 
which we will refer to as 
\textit{intertask-food-objects}, workers were assigned to either a
\textit{food} or \textit{objects} treatment.  Workers in these treatments
performed a set of five \textit{initial tasks}, which each involved 
providing five descriptive labels for an image depicting 
either food or (non-food) objects, depending on the worker's 
treatment (see Fig.~\ref{fig:task}A and B).  Following the initial 
tasks, workers performed five \textit{test tasks}, which were identical for 
both treatments.  The test tasks contained images depicting a 
mixture of food and other objects (see Fig.~\ref{fig:task}C), and workers
were again asked to supply five labels.  Five initial 
tasks, together with the test tasks, comprised one HIT 
(\# workers were only allowed to participate once). During the HIT, workers 
were presented images one at a time, and, crucially, there was no distinction
or interruption between the initial and test tasks.

A $\chi^2$ test shows that the frequency of word usage by
workers in the \textit{food} and \textit{objects} treatments differed
significantly during test tasks ($p = 6.0 \times 10^{-14}$), even though the test tasks were identical 
in both treatments (\# see supplementary text for tabulated statistics).  This shows that earlier tasks have a 
significant effect on later ones, and raises concerns about the 
design of microtasks, and possibly the microtask methodology itself.

While this affirms the \textit{existence} of intertask effects, we wish to
understand the nature and severity of the bias induced by prior task 
exposures.  
We define the extent of bias, $\theta$, induced by alternative exposures, to 
be the resulting change in the probability with which workers provide given 
responses (formally the totatal variation distance):
\begin{equation}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p_1(x) - p_2(x) \right|,
\end{equation}
where $p_i(x)$ is the probability that a worker subjected to treatment $i$
provides response $x$, from the set of possible responses $X$.
The problem of determining $\theta$ from finite samples of responses is 
difficult, which leads us to reformulate it as a classification problem: 
given a worker's 
response, can a machine reliably infer what her priming exposure had been?  
Intuitively, the greater the effect that priming exposures have on workers' 
responses, the more accurate the classifier can be.  Formally, as we show
in the supplementary text, the performance of such a classifier, $\eta$,
yields a lower bound on the true bias:
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
Thus, measuring the performance of a classifier allows us to establish a
lower bound on the extent of bias. This approach can be used to bound the 
bias induced by any perturbation, including both intertask effects and 
framing.  As we have defined it, bias ranges from 0 (meaning the exposures 
do not affect the probabilities of respnoses), to 1 
(or 100\%) (meaning that under different exposures, workers provide completely
different sets of responses).

@@

Using a na\"ive Bayes classifier (\# in the 
supplementary material we discuss the choice of classifier, the
approach to measuring accuracy, and draw a comparison to the results obtained 
if a support vector machine is used.), we found that intertask effects 
lead to a 30\% bias between workers from the \textit{food} and 
\textit{objects} treatments.

As mentioned, the effects of framing on workers' responses to microtasks has 
been studied in various ways 
\cite{Kinnaird2012281,chandler2013breaking,thibodeau2013natural}.
Therefore, as a point of comparison, we performed a similar experiment 
in which we framed the purpose of the tasks.  Workers were either told that 
the tasks were ``Funded by the laboratory for the visual perception of Food 
and Ingredients'', or ``\ldots of Objects and Tools''.  We did not observe a 
statistically significant framing-induced bias, using a na\"ive Bayes 
classifier (see Fig.~\ref{fig:theta}).  This suggests
that prior task exposure is a stronger priming modality than framing.
\td{I need to talk about the $\chi^2$ result here.}

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (\#) (see Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin 
(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
strong bias as a result of intertask effects (about 50\%) 
(see Fig.~\ref{fig:theta}A).  Again, we compared intertask effects to 
framing, by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or cultures.  
For this framing experiment, we did not observe a statistically significant 
difference between the labels attributed by the \textit{food} and 
\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).

@@

\begin{figure}
	\centering
	\includegraphics[scale=1]{figs/theta.pdf}
	\caption{
		Bias as measured by a na\"ive Bayes classifier, $\theta_\mathrm{NB}$,
		induced in image-labeling tasks, due to framing and 
		intertask effects. 
		(A) Bias in the responses to five test tasks,
		measured between the pairs of treatments indicated on the $x$-axis.  
		(B) Bias between the treatments of \textit{task1}, 
		measured for individual test tasks, and plotted as a function of 
		task position.  Error bars show the 95\% confidence intervals.
	}
	\label{fig:theta}
\end{figure}

@@

To better understand the nature of 
intertask effects, we investigated the vocabulary
that workers used to label test tasks. A natural expectation is that, within
a given experiment, the food-primed workers would use more food-related words 
than their non-food-primed counterparts.  However, this was not generally 
the case. In the \textit{intertask-food-culture} experiment, food-primed
workers actually used significantly \textit{fewer} food-related words 
during test tasks
(\# food related words were identified using the wordnet corpus, augmented
with additional words obtained by crawling a recipe website (see supplementary
information for details)) (see Fig.~\ref{fig:specificity}).  This finding
rules out a simple mechanism in which worker's attention is drawn toward
content that had been found in earlier tasks.  Seeing content in prior tasks 
seems to affect the probability that a worker refers to that content it in 
subsequent tasks, but does not necessarily increase it.

To deepen our understanding, we investigated workers' lexical richness in 
reference to food, that is, the number of \textit{unique} food-related words
used.
Both \textit{intertask} experiments showed that food-exposed workers had 
greater lexical richness, in reference to food, than their non-food-primed 
counterparts (as much as 20\% more; see Fig.~\ref{fig:specificity}).  This
held in the case of \textit{intertask-food-culture}, even though, in that 
experiment, food-primed workers referred to food less often overall.  
This enrichment of the food-related lexicon 
was also observed in the \textit{priming-food-objects}, and 
\textit{echo-food-objects} experiments, but to a lesser extent.

@@

\subsection*{S3: Additional results not shown in the main text}
\paragraph{Testing intertask and framing effects using 
	Pearson's $\chi^2$ test of homogeneity.
}
To test whether intertask and framing effects induced statistically 
significant changes in word frequencies, we assembled a contingency table
for each experiment, containing the frequencies of words in each treatment
for a given experiment.  Any words that appeared less than 10 times for
an experiment (i.e. appearing less than 5 averaged over each treatment)
were lumped together into a separate `OTHER' category, to ensure validity
of the test.  The degrees of freedom, test statistic, and $p$-values were
then calculated according to Pearson's $\chi^2$ test, using 
Yate's correction.  Results are tabulated in Table~\ref{table:chi2}.
All experiments showed significant changes in word-frequencies in response
to the task or framing exposures, at $\alpha=0.05$, leading us to 
reject the null hypothesis that the priming exposures had no effect.
Note, however, that while the other tests showed very high significance, 
\textit{frame-food-culture} was marginally significant.  This is consistent 
with our finding weak effects for \textit{frame-food-culture}, throughout our 
results.

The use of Pearson's $\chi^2$ test has been criticized in linguistic 
applications, due to the finding that many corpuses are not themselves
homogeneous \cite{kilgarriff1996comparing}.  
This results from the fact that corpuses are made of many
distinct texts, together with the fact that words tend to come in bursts.
When a rare word is encountered in a given text, it is much more likely
to be encountered again in the same text, which making the word's frequency
within the text far from the average.  As a result,
if a corpus is randomly split, putting half of the texts in one set, 
and half in another, there can be a significant non-homogeneity between the 
two halves, when tested using Pearson's $\chi^2$ test.  Thus, finding two
corpuses to be different might simply be an artifact of the corpus' own
inhomogeneity.

We don't expect this to be a concern in our case, because the ``texts'' are 
individual responses from workers, which will not, in general, be subject to 
the burstiness phenomenon.  But to test this, we randomly divided the workers 
from each experimental treatment into two sets, and tested the homogeneity 
between these sets.  Results are tabulated in Table~\ref{table:chi2_within}, 
and show that treatments 
\textit{are} homogeneous.  Thus, the lack of homogeneity \textit{between} 
the treatments of given experiments can be attributed to the framing / 
intertask effects.

\begin{table}
\centering
\begin{tabular}{c c c c}
\toprule
Experiment & Degrees of freedom & $\chi^2$ & $p$-value\\
\toprule
\textit{intertask-food-objects} & 117 & 268.7 & $6.0 \times 10^{-14}$\\
\textit{frame-food-objects} & 116 & 167.8 & $1.2 \times 10^{-3}$\\
\textit{echo-food-objects} & 126 & 381.3 & $1.7 \times 10^{-27}$\\
\textit{intertask-food-culture} & 120 & 447.5 & $2.8 \times 10^{-39}$\\
\textit{frame-food-culture} & 119 & 127.2 & $0.29$\\
\bottomrule
\end{tabular}
\caption{
	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
	between treatments from each experiment.  This shows that the treatments
	significantly affected word usage, 
	except in the case of \textit{frame-food-culture}.
}
\label{table:chi2}
\end{table}

\begin{table}
\centering
\begin{tabular}{c c c c c}
\toprule
Experiment & Treatment & Degrees of freedom & $\chi^2$ & $p$-value\\
\toprule
\noalign{\smallskip}
\multirow{2}{*}{\textit{intertask-food-objects}} & \textit{food} & 65 & 39.0 & $1.0$\\
 & \textit{objects} & 65 & 53.2 & $0.85$\\
\noalign{\smallskip}
\multirow{2}{*}{\textit{frame-food-objects}} & \textit{food} & 67 & 41.3 & $0.99$\\
 & \textit{objects} & 62 & 66.9 & $0.31$\\
\noalign{\smallskip}
\multirow{2}{*}{\textit{echo-food-objects}} & \textit{food} & 66 & 40.9 & $0.99$\\
 & \textit{objects} & 66 & 35.6 & $1.0$\\
\noalign{\smallskip}
\multirow{2}{*}{\textit{intertask-food-culture}} & \textit{food} & 62 & 65.9 & $0.34$\\
 & \textit{culture} & 68 & 57.2 & $0.82$\\
\noalign{\smallskip}
\multirow{2}{*}{\textit{frame-food-culture}} & \textit{food} & 57 & 49.6 & $0.75$\\
 & \textit{culture} & 64 & 55.1 & $0.78$\\
\noalign{\smallskip}
\bottomrule
\end{tabular}
\caption{
	Results for Pearson's $\chi^2$ test of homogeneity of the word-frequencies
	within treatments, which were randomly partitioned for the test.  This
	shows that word-usage within treatments is homogeneous.
}
\label{table:chi2_within}
\end{table}

\paragraph{Most suppressed / activated terms.}
The words whose frequencies differed most between the treatments of given 
experiments are shown in Table~\ref{table:top-words}.  Note that 
the word that was most suppressed in food-exposed treatments was always 
``food''.

@@

	\end{tabular}
	\caption{
		Top 5 words, used to label the first test image, whose usage frequency
		increased or decreased the most between treatments of given 
		experiments.  Positive values indicate that the food-exposed treatment
		used the word with higher frequency.  Word frequencies for 
		\textit{intertask-food-objects} are aggregated accross 5 
		permutations, and hence tend to show larger absolute differences.
	}
	\label{table:top-words}
\end{table}

@@

	Before performing any analysis on the labels that workers provided, we
	performed a series of preprocessing steps.  
	Labels that contained
	multiple words (separated by spaces or punctuation) were split, with
	punctuation removed, and the separated words were treated as distinct 
	features in subsequent analysis.
	Misspelled words were automatically corrected using a spelling 
	correction algorithm described below.  
	Next, words were lematized using the
	wordnet lemmatizer \cite{miller1995wordnet,felbaum1998wordnet}.  
	Common words such as ``the'', ``to'', or ``with'', were found using the
	the NLTK's English stop-word list and removed \cite{loper2002nltk}.

@@

	\paragraph{Crawling the world food section of allrecipes.com.}
	The website allrecipes.com was accessed on 3-4 November 2014 using 
	automated scripts.  A total of 2642 recipe listings and 15621 recipe
	instruction pages were retrieved.  Recipe listings were pages that 
	provided lists of recipes, and contained a title and short description 
	for each.  
	The recipe instruction pages had lists of ingredients and preparation 
	instructions.  All of the words found in recipe titles, short
	descriptions, ingredients lists, and preparation instructions were
	collected, and saved as an auxiliary set to augment the \textit{legal set}
	used in spelling correction.

@@

We chose the synsets \texttt{food.n.01} and \texttt{food.n.02} to act as roots
in defining which words should be considered food-related.  Any word form
belonging to a synset which was a hyponym of one of the two root synsets
identified above was considered to be a reference to food.  Here, as in the
main text, when we say hyponym, we mean either a direct hyponym, or a hyponym
of a hyponym, and so on.

@@

The subset of the wordnet corpus induced by the hyponyms of \textit{food.n.01}
and \textit{food.n.02} provide a set of 3590 words.  Manual
testing showed good coverage, except for references to ethnic foods.  
Since, especially in \textit{exp2}, we had images containing many ethnic 
foods, we decided to augment the wordnet corpus with words learned by 
crawling the world food section of the allrecipes.com website.

After collecting a set of words using an automated script 
(described above), we collected the set of words that had been used by
workers and which had been seen during crawling of the allrecipes.com website,
but which were not included in wordnet.  We grafted these extra words into
the wordnet hyponym-hypernym graph manually, which ensured that any references
to ethnic words learned from crawling would be properly classified as 
food references.

\paragraph{Validation of the detection of food references.}
To determine whether our extended version of wordnet provided a good approach
to detecting food-related words, we sampled 500 words 
(50 from each test task)  from the set of labels produced by workers and had 
three human coders manually decide if they were 
food-related or not.

The coders were instructed to consider whether a word was a noun signifying
an edible item.  The guiding principle was, for the coder to ask herself,
``can I eat X'', where X is the word she is coding.  The coders were
shown the used in the task from which the word came, to help resolve ambiguity
in the sense of the word that had been given.  Coders were also shown the 
spelling correction (if any) that the spell-correction algorithm had made,
to help interpret misspelled words.

@@

	\textit{Spelling correction.}  Because we used free-text
	entry for the labels, there was bound to be many spelling mistakes.
	This would tend to reduce the accuracy of a classifier, because the 
	entries ``bread'' and ``braed'' would be regarded as completely different
	features, even though they clearly correspond to the same 
	\textit{intended word}.  While no algorithm can determine a worker's 
	intentions, it is possible to check words against a corpus, and, in the
	case of a misspelled word, look for plausible corrections based on 
	edit distance.

@@

	\textit{Splitting multiple words.}  Although workers were 
	instructed to put one word per text input, many put multiple words.
	Theoretically the original multi-word entry might bear additional 
	information that could be useful in discerning a worker's exposure. 
	In practice, it would be necessary for that word combination to recur,
	which is unlikely.  Therefore we chose to split multi-word entries,
	using the individual words as features.  This meant that the outputs of
	some workers generated more features than those of others.
